Research Proposal

### 2021-10-17 Reports/JOURNAL - Confidence Regions/IT-ConfidenceRegionsR1.tex
R1 recuperada e em edição

\usepackage[binary-units]{siunitx}
\usepackage{bm,bbm}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{float}
\usepackage{rotating}
\graphicspath{{./Figures/}}
\usepackage[linesnumbered,lined,boxed]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
\makeatother
\usepackage{undertilde}
\usepackage{todonotes}
\usepackage{comment}

@@

\author[1]{Eduarda T.\ C.\ Chagas}
\author[2,3]{Marcelo Queiroz}
\author[4]{Osvaldo A.\ Rosso}
\author[1]{Heitor S.\ Ramos}
\author[2]{Cristopher G.\ S. Freitas}
\author[2]{Leonardo V.\ Pereira}
\author[4]{Alejandro C.\ Frery}

@@

\begin{abstract}
The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series, 
by computing Information Theory descriptors of the histogram of ordinal patterns.
Such descriptors lie in a 2D manifold: the Entropy-Complexity plane.
This article proposes the first approach that uses the entropy-complexity plane to test the white noise hypothesis.
Our test is based on true white noise sequences obtained from physical devices.
The proposed methodology provides consistent results, 
managing to assess sequences of true random samples as random (adequate size), 
rejecting correlated sequences (sound power), and
capturing the randomness of generators previously analyzed in the literature.
\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
\end{abstract}

>>>>

\usepackage[binary-units]{siunitx}
\usepackage{bm,bbm}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{float}
\usepackage{rotating}
\graphicspath{{./Figures/}}
\usepackage[linesnumbered,lined,boxed]{algorithm2e}
\makeatletter
\renewcommand{\@algocf@capt@plain}{above}% formerly {bottom}
\makeatother
\usepackage{undertilde}

\usepackage{todonotes}
\usepackage{comment}

@@

\author[1]{Eduarda T.\ C.\ Chagas}
\author[2,3]{Marcelo Queiroz-Oliveira}
\author[4]{Osvaldo A.\ Rosso}
\author[1]{Heitor S.\ Ramos}
\author[2]{\mbox{Cristopher G.\ S. Freitas}}
\author[5]{Alejandro C.\ Frery}

@@

\begin{abstract}
The \citeauthor{PermutationEntropyBandtPompe} methodology has been used successfully in the analysis of time series. 
It consists of computing
Information Theory descriptors of the histogram of ordinal patterns. 
Such descriptors lie in a 2D manifold: the Entropy-Complexity plane. 
This article provides the first proposal
of a test in the Entropy-Complexity plane for the
white noise hypothesis.
Our test is based on true white noise sequences obtained from physical devices.
The proposed methodology provides consistent results, 
managing to assess sequences of true random samples as random (adequate size), 
rejecting correlated sequences (sound power), and
capturing the randomness of generators previously analyzed in the literature.
\keywords{Random number generators, Bandt–Pompe approach, Entropy-complexity plane, Time Series, Information Theory}
\end{abstract}

### 2021-10-17 Reports/Journal - Confidence Regions/Chapters/Background.tex
R1 recuperada e em edição

The first descriptor is a measure of the disorder of the system.
The most frequently used feature for this is the Normalized Shannon entropy, defined as
\begin{equation}
	H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
\end{equation}
with the convention that terms in the summation for which $h(j)=0$ are null.
This quantity is bounded in the unit interval. 
It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability distribution function).

Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
They employed the Euclidean distance between $\bm h$ and the uniform probability distribution function.

>>>>

The first descriptor is a measure of the disorder of the system.
The most frequently used feature for this is the Normalized Shannon entropy, defined as
\begin{equation}
	H(\bm h) = -\frac{1}{\log D!} \sum_{j=1}^{D!} h(j) \log h(j),
\end{equation}
with the convention that terms in the summation for which $h(j)=0$ are null.
This quantity is bounded in the unit interval. 
It is zero when $h(j)=1$ for some $j$ (and, thus, all other bins are zero), and one when $h(j)=1/D!$ for every $j$ (the uniform probability function).

Although very expressive, the Normalized Shannon Entropy is not able to describe all possible underlying dynamics.
In particular, for intermediate values of $H$, there is a wide variety of situations worth characterizing.
To this aim, \citet{LopezRuiz1995} proposed using the disequilibrium  $Q$, a measure of how far $\bm h$ is from an equilibrium or noninformative distribution.
They employed the Euclidean distance between $\bm h$ and the uniform probability function.

The Jensen-Shannon distance between $\bm h$ and the probability function $\bm u=(u(1), u(2), \dots, u(D!))$ stems as a more adequate measure of such a distance:
\begin{equation}
	Q'(\bm{h}, \bm{u}) = \sum_{\ell=1}^{D!} \Big(h(\ell) \log\frac{h(\ell)}{u(\ell)} +
	u(\ell) \log\frac{u(\ell)}{h(\ell)}
	\Big).
	\label{eq:JensenShannon}
\end{equation}
This has been the preferred distance function since its proposal by \citet{Lamberti2004}.
Most works consider the uniform distribution $\bm u = (1/D!, 1/D!, \dots, 1/D!)$ as the reference model.

The quantity~\eqref{eq:JensenShannon} is also called ``disequilibrium.''
The normalized disequilibrium is $ Q=Q'/\max\{Q'\}$, and we chose to work with the uniform probability distribution function as the equilibrium law.
\textcolor{red}{[Eduarda:] alguma referência (dentre as que já citamos) e algumas propriedades? Alguma simplificação quando u é a uniforme?}
